\large COOPERATIVE 3-D MAP GENERATION USING MULTIPLE UAVS

### 2015-04-26 draft.tex
Progress on the hardware and design decisions.

\documentclass[letterpaper, oneside, 12pt]{report}
\usepackage[margin = 1.0in]{geometry}
\usepackage[nottoc,notlof,notlot]{tocbibind}
\usepackage[colorlinks=false]{hyperref}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{setspace}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{cite}
\usepackage{newcent}

\geometry{letterpaper}
\renewcommand{\familydefault}{\sfdefault}

@@

\begin{document}
\doublespacing

@@

\section{Literature Review}

@@

\chapter{Hardware Design}

@@

\begin{table}[h!]
\centering
\caption{List of Components}
\vspace{2mm}
\begin{tabular}{l l}
\hline \hline
\vspace{-2mm}
Component & \multicolumn{1}{l}{Description} \\ [1ex]
\hline
& \\
ODROID XU3 & ARM SBU \\
Pixhawk PX4 & Controller \\
Microsoft Kinect & Visual Sensor \\
MaxSonar EZ0	& Sonar Sensor \\
\end{tabular}
\end{table}

>>>>

\documentclass[letterpaper, oneside, 10pt]{report}
\usepackage[margin = 1.0in]{geometry}
\usepackage[nottoc,notlof,notlot]{tocbibind}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{setspace}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{cite}
\usepackage{classicthesis}

\geometry{letterpaper}

@@

\begin{document}
% \doublespacing

@@

\section{Overview}
\section{Literature Review}

@@

\chapter{Robot Design}

\section{Design Decisions}

Several key design decisions arose when choosing a direction for robot design and selection of components. The most signifcant choice for the robot was choosing an architecture for the onboard computational unit - specifically an ARM or x86 computer. The second key design dilemma involved the selection of a laser-scanning sensor or an RGB-D camera. As shown below, both these choices had great effect upon the path of experimentation and results obtained.

\subsection{ARM vs. x86}

The main advantage of choosing an x86 board (found in most desktop or laptop computers) is compatibility. Almost all software packages are available in prebuilt, binary form on package managers (such as Ubuntu's apt-get) and setting up the computing environment can be done with a few simple installation commands. This convenience, unfortunately, comes at a financial and dimensional price - most small form-factor x86 boards are extremely expensive and cheaper options are considerably larger in size. These tradeoffs make selection of such a board unfeasible for an aerial drone where space is extremely limited and minimization of cost is a primary concern. As a result, ARM boards (like those in smartphones) are much more attractive - they offer extremely small form-factors, yet remain very affordable. The issue that arises, of course, is that of compatibility - many programs or libraries are not (immediately) available on an ARM installation and require manual compilation of source code using an ARM-based compiler and possible changes to the source code itself first.

\subsection{Laser vs. RGB-D Camera}

\section{Hardware}

The hardware design of the robot was focused on using low-cost, off-the-shelf components (see Table 1). The approximate cost of a built robot was \$894, significantly cheaper than those used at MIT or University of Washington with similar project requirements.

% Table of components used on robot
\begin{table}[h!]
  \centering
  \caption{Table of Components}
  \vspace{2mm}
  \begin{tabular}{l l l}
    \hline \hline
    \vspace{-2mm}
    Component & \multicolumn{1}{l}{Description} & \multicolumn{1}{l}{Cost} \\ [1ex]
    \hline
    & \\
    DJI F450 Frame & Chassis & \$200 \\
    DJI 1045 Propellers & Props & \$10 \\
    DJI 2212 Motors & Actuators & \$30 \\
    12V and 5V Regulators & Power Reg. & \$40 \\
    Zippy 2450 mAh LiPo & Battery & \$30 \\
    64GB ODROID XU3 & ARM SBU & \$240 \\
    Pixhawk PX4 & Controller & \$220 \\
    Microsoft Kinect & Visual Sensor & \$99 \\
    MaxSonar EZ0	& Sonar Sensor & \$25 \\
  \end{tabular}
\end{table}

\noindent The robot used a stock F450 frame from DJI, which was not modified in any way - all components were mounted on existing areas using screws or adhesive products.

\begin{figure}[h!]
 \caption{Photograph of finished quadcopter robot.}
 \centering
   \includegraphics[width=0.3\textwidth]{figures/quadcopter}
\end{figure}

\section{Software}

@@

\chapter{Single Robot}
\section{Navigation}
\section{Mapping}
\section{Results}

\chapter{Multiple Robots}
\section{Map Fusion}
\section{Results}

\chapter{Conclusions}

\chapter{Appendix}
